Towards atomistic resolution structure of phosphatidylcholine glycerol backbone and choline headgroup at different ambient conditions\footnote{Publication about results presented in the NMRlipids project}

### 2015-05-07 HGmodelMANUSCRIPT/HGmodel_ACStemplate.tex
Mention data management in Hubert Santuz contribution
typo fix

AB and CL acknowledges financial support from the French National Research Agency
(ANR: “Biolubrication by phospholipid membranes” Bioub2012) and
computing time allocation from P{\^o}le Scientifique de Mod{\'e}lisation Num{\'e}rique from the ENS Lyon (PSMN),
and Centre Informatique National de l'Enseignement Sup{\'e}rieur (CINES, Montpelier, France)
(Project c2015096850).
FFR acknowledges CONACYT and DGAPA UNAM IG100513
for financial support, Cluster H\'ibrido de Superc\'omputo Xiuhcoatl - CINVESTAV and Miztli - UNAM for computational resources. 
MJ and JT acknowledge and CSC - IT Center for Science for computational resources (project number tty3979).
MJ also acknowledges the Finnish Doctoral Programme in Computational Sciences (FICS) for funding.
JT, MJ, TR and WK acknowledge the funding from the Academy of Finland (Centre of Excellence program) 
and the European Research Council (Advanced Grant project CROWDED-PRO-LIPIDS).
WK acknowledges CSC -- IT Centre for Science (Espoo, Finland) is acknowledged for excellent computational resources (project number tty3995).
MSM acknowledges financial support from the Volkswagen Foundation (86110).
LM acknowledges funding proved by the Institut national de la sant\'e et de la recherche m\'edicale (INSERM).
JM acknowledges CSC -- IT Center for Science for computational resources.
OHSO acknowledges Tiago Ferreira and Paavo Kinnunen for useful discussions, 
the Emil Aaltonen foundation for financial support, 
Aalto Science -- IT project and CSC -- IT Center for Science for computational resources. 
HS acknowleges Catherine Etchebest and St\'ephane T\'eletch\'ea for useful discussions and continued support, the HPC 
resources granted from GENCI-CINES (Grant 2014-c2014077209) and computer facilities provided by R\'egion Ile de France and INTS (SESAME 2009 project).

@@

\subsection{Author Contributions}
{\it Alexandru Botan} provided simulation results for charmm36-UA\\
{\it Fernando Favela} prepared, performed and analyzed simulations
with popc and cholesterol for the CHARMM36 All-Atom FF. \\
{\it Patrick F. J. Fuchs} Ran and analyzed the Poger simulations. Provided scientific information which significantly advanced the project (signs and forking of order parameters). \\
{\it Matti Javanainen} prepared and performed simulations with multiple lipid models and analyzed the results. Supervised the work of JT.\\
{\it Matej Kanduc} provided simulation results for the Berger DLPC model \\
{\it Waldemar Kulig} prepared the MD simulations with cholesterol for the MacRog FF \\
{\it Antti Lamberg} Prepared and performed simulations with Berger and its variants to show the importance of the signs and stereospecific labeling of the order parameters. \\
{\it Claire Loison} provided simulation results for charmm36-UA. \\
{\it Alexander Lyubartsev} provided simulation results for Högberg08 force field.\\
{\it Markus S. Miettinen} \todo{Please write a text summarizing your contribution} \\
{\it Luca Monticelli} Critical discussions in all phases of the project. Collaboration with Jukka  M{\"a}{\"a}tt{\"a}. \\
{\it Jukka M{\"a}{\"a}tt{\"a}}  prepared and performed simulations with Berger and Slipids models and analyzed the results.\\
{\it O. H. Samuli Ollila} Designed and managed the work. Ran and analyzed several simulations. Wrote the manuscript.  \\
{\it Marius Retegan} Prepared and validated the GROMACS compatible parameter files for GAFFlipid and Lipid14 force fields.\\
{\it Tomasz Rog} Provided the topologies for the MacRog model and also the full hydration simulation data with this model. \\
{\it Hubert Santuz} prepared and performed the cholesterol simulations with CHARMM36 and analyzed the results. \\
{\it Joona Tynkkynen} prepared and performed the dehydration simulations with the MacRog FF.\\

>>>>

AB and CL acknowledges financial support from the French National Research Agency
(ANR: “Biolubrication by phospholipid membranes” Bioub2012) and
computing time allocation from P{\^o}le Scientifique de Mod{\'e}lisation Num{\'e}rique from the ENS Lyon (PSMN),
and Centre Informatique National de l'Enseignement Sup{\'e}rieur (CINES, Montpelier, France)
(Project c2015096850).
FFR acknowledges CONACYT and DGAPA UNAM IG100513
for financial support, Cluster H\'ibrido de Superc\'omputo Xiuhcoatl - CINVESTAV and Miztli - UNAM for computational resources. 
MJ and JT acknowledge and CSC - IT Center for Science for computational resources (project number tty3979).
MJ also acknowledges the Finnish Doctoral Programme in Computational Sciences (FICS) for funding.
JT, MJ, TR and WK acknowledge the funding from the Academy of Finland (Centre of Excellence program) 
and the European Research Council (Advanced Grant project CROWDED-PRO-LIPIDS).
WK acknowledges CSC -- IT Centre for Science (Espoo, Finland) for excellent computational resources (project number tty3995).
MSM acknowledges financial support from the Volkswagen Foundation (86110).
LM acknowledges funding proved by the Institut national de la sant\'e et de la recherche m\'edicale (INSERM).
JM acknowledges CSC -- IT Center for Science for computational resources.
OHSO acknowledges Tiago Ferreira and Paavo Kinnunen for useful discussions, 
the Emil Aaltonen foundation for financial support, 
Aalto Science -- IT project and CSC -- IT Center for Science for computational resources. 
HS acknowleges Catherine Etchebest and St\'ephane T\'eletch\'ea for useful discussions and continued support, the HPC 
resources granted from GENCI-CINES (Grant 2014-c2014077209) and computer facilities provided by R\'egion Ile de France and INTS (SESAME 2009 project).

@@

\subsection{Author Contributions}
{\it Alexandru Botan} provided simulation results for charmm36-UA\\
{\it Fernando Favela} prepared, performed and analyzed simulations
with popc and cholesterol for the CHARMM36 All-Atom FF. \\
{\it Patrick F. J. Fuchs} Ran and analyzed the Poger simulations. Provided scientific information which significantly advanced the project (signs and forking of order parameters). \\
{\it Matti Javanainen} prepared and performed simulations with multiple lipid models and analyzed the results. Supervised the work of JT.\\
{\it Matej Kanduc} provided simulation results for the Berger DLPC model \\
{\it Waldemar Kulig} prepared the MD simulations with cholesterol for the MacRog FF \\
{\it Antti Lamberg} Prepared and performed simulations with Berger and its variants to show the importance of the signs and stereospecific labeling of the order parameters. \\
{\it Claire Loison} provided simulation results for charmm36-UA. \\
{\it Alexander Lyubartsev} provided simulation results for Högberg08 force field.\\
{\it Markus S. Miettinen} \todo{Please write a text summarizing your contribution} \\
{\it Luca Monticelli} Critical discussions in all phases of the project. Collaboration with Jukka  M{\"a}{\"a}tt{\"a}. \\
{\it Jukka M{\"a}{\"a}tt{\"a}}  prepared and performed simulations with Berger and Slipids models and analyzed the results.\\
{\it O. H. Samuli Ollila} Designed and managed the work. Ran and analyzed several simulations. Wrote the manuscript.  \\
{\it Marius Retegan} Prepared and validated the GROMACS compatible parameter files for GAFFlipid and Lipid14 force fields.\\
{\it Tomasz Rog} Provided the topologies for the MacRog model and also the full hydration simulation data with this model. \\
{\it Hubert Santuz} prepared and performed the cholesterol simulations with CHARMM36 and analyzed the results. 
Made significant contribution in the data management of the project.\\
{\it Joona Tynkkynen} prepared and performed the dehydration simulations with the MacRog FF.\\
